Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/background.tex
applying comments

\subsection{Terminology and Notation}
%We will start by introducing several concepts used by the IFDS and IDE analyses.
\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
$n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
\end{mdelete}
%and edges represent transfer of control between the instructions during an execution of the program. 
%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
%An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure. By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures. 
The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
%is a control-flow graph
%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.

@@

The output of the IDE algorithm is, for each node $n$ in the supergraph,
the \textit{meet-over-all-valid-paths} solution
  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
  \mtodo{I like that the text is now very compact. But I wonder if some of the formulas should be put
  on a separate line and enumerated. For example, I need to reference the definition of $\textsf{MVP}_{\textsf{Env}}$ in the
  proof, but since it's embedded in the text, I'm repeating the formula in the appendix and reference the section. Is that fine?}
where $M_\textsf{Env}$ is extended from edges to paths by composition.

>>>>

\subsection{Terminology and Notation}
%We will start by introducing several concepts used by the IFDS and IDE analyses.
The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
$n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
%and edges represent transfer of control between the instructions during an execution of the program. 
%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
%An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure. By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures. 
The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
%is a control-flow graph
%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.

@@

The output of the IDE algorithm is, for each node $n$ in the supergraph,
the \textit{meet-over-all-valid-paths} solution
  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
where $M_\textsf{Env}$ is extended from edges to paths by composition.

### 2014-12-12 content/example.tex
applying comments

In this section, we illustrate our approach using a small motivating example that
shows how our technique can be used to improve the precision of taint analysis.
A taint analysis is a specialized dataflow analysis for computing how string values
may flow from ``sources'', which are typically statements that read untrusted input, 
to ``sinks'', which are typically securitive-sensitive operations such as calls to 
a database. In previous research \TODO{cite}, taint analysis algorithms have been 
formulated as IFDS problems.

>>>>

In this section, we illustrate our approach using a small motivating example that
shows how our technique can be used to improve the precision of taint analysis.
A taint analysis is a specialized dataflow analysis for computing how string values
may flow from ``sources'', which are typically statements that read untrusted input, 
to ``sinks'', which are typically security-sensitive
operations such as calls to 
a database. In previous research \TODO{cite}, taint analysis algorithms have been 
formulated as IFDS problems.

### 2014-12-12 content/impl.tex
applying comments

\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
\otodo{we agreed to move this figure to the initial example section}
  \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}

@@

  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.

On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $\psi$ to \code v.

@@

\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}\mtodo{I changed the formalisms in this section. Please see if you agree to these changes.}

>>>>

\otodo{we agreed to move this figure to the initial example section}
  \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}

@@

  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\Lambda$-fact to the method's return value $r$. 
  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.

On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $r$ to \code v.

@@

\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}
